Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review]}

### 2022-10-10 paper/Paper.tex
small fix
complen -> cplen, other minor changes to section 3

%KYR: not necessary for TACAS; the audience alraedy knows this
%% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
%% An MLTL formula $\alpha$ is in \emph{negation normal form} if
%% \begin{itemize}
%%     \item Any negation symbols appear only in front of propositional variables.
%%     \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
%%     \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
%% \end{itemize}
%% \end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MLTL Regular Expressions} \label{regex}
We add to the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of a MLTL formula.
\begin{definition}[\emph{Temporal Regular Expression}]
Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$. Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula. We use the following operations to describe the form of satisfying computations of the formula in the bit string representation:
\begin{itemize}
  \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
%    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
    \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
    \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length. Note that in the bit string representation, $(,S^n)$, denotes a time step in which the truth value of all $n$ propositional variables does not matter.
    \item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
      \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$. %KYR: is this one relevant or should we take it out?
    \item We do not use the Kleene star since our computations are a fixed finite length.
\end{itemize}
\end{definition}
An example of these operations follows.
\begin{example}
Let there be $n = 2$ propositional variables, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$). Clearly $T$ is the longer regex by one time step, so we concatenate $,S^2$ to the right of $R$. Thus $T =1S,1S | S1,S1$ and $R = S1,SS$. Now the regexes are the same length, so we can perform set intersection and alternation:
\begin{itemize}
    \item $R \land T = 11,1S | S1, S1$.
    \item $R \lor T = S1,SS | 1S,1S | S1,S1 = S1,SS | 1S,1S$.
\end{itemize}
\end{example}

For the purposes of describing the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\alpha, \beta$ well-formed MLTL formulas in negation normal form. We define the regular expression of satisfying computations for an MLTL formula as follows:
 \begin{align}
     &\text{reg}(\top) = S^n\\
     &\text{reg}(\bot) = \emptyset \\
     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
    &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
 \end{align}

 \subsection{Minimum Computation Length}
 These regular expressions describe all the satisfying computations of an MLTL formula of length $\text{complen}(\alpha)$, which is defined recursively below:
\begin{align}
    &\text{complen}(p_k) = \text{complen}(\neg p_k) = 1\\
    &\text{complen}(\alpha \land \beta) = \text{complen}(\alpha \lor \beta) = \max(\text{complen}(\alpha), \text{complen}(\beta))\\
    &\text{complen}(\mathcal{G}_{[a,b]} \alpha) = \text{complen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{complen}(\alpha)\\
    &\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))
\end{align}

Intuitively, $\text{complen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature. In \cite{KZJZR20}, $$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha), \text{complen}(\beta))$$

whereas our minimum computation length for Until and Release is 
$$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{complen}(\alpha)-1}, \text{complen}(\beta)).$$
We provide the proof for the minimum computation length of Until and Release below.
\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\alpha, \beta$ be well-formed MLTL formulas in NNF. The minimum computation length of Until and Release is given by $\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))$.
\end{theorem}

\begin{proof}
The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\
 Recall that $\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$. Thus
 \begin{align*}
     \text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{complen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{complen}(\alpha), i + \text{complen}(\beta))\right)\\
     &= \max_{a \leq i \leq b} \left(i + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta))\right)\\
     &= b + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta)).
 \end{align*}
 Now recall that $\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$. Thus
 \begin{align*}
     \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{complen}(\mathcal{G}_{[a,b]} \beta), \text{complen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
     &= \max\left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
     &= \max \left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{complen}(\beta), i + \text{complen}(\alpha))\right) \right)\\
     &= \max \left( b + \text{complen}(\beta), \max(b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\right)\\
     &= \max(b + \text{complen}(\beta), b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\\
     &= b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta)).
 \end{align*}
 This completes the proof.
 \end{proof}

@@

 \begin{theorem}[\emph{Soundness and Completeness}]
 For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{complen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
 \end{theorem}
 \begin{proof}
 We proceed by induction on the length of the formula.\\

@@

 \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
 If $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$. Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

 \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
 Since $|\pi| = \text{complen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{complen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

@@

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} >  \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} > \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \lor \text{''} + \alpha_{2} + \text{``)''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} > \alpha_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} = \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} = \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = 
    \text{``((''} + \alpha_{1} + \text{``} \& \text{''} + \alpha_{2} + \text{``)}
    \lor 
    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2}) + \text{``))''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} = \alpha_{2})) =
    S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})) \; + \;  
    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\lor$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\lor [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \lor \alpha_{2}) \lor ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\lor$, we have that:
    \[
    S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\&$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\& [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \& \alpha_{2}) \& ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\&$, we have that:
    \[
    S(\text{\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}

>>>>

%KYR: not necessary for TACAS; the audience already knows this
%% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
%% An MLTL formula $\alpha$ is in \emph{negation normal form} if
%% \begin{itemize}
%%     \item Any negation symbols appear only in front of propositional variables.
%%     \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
%%     \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
%% \end{itemize}
%% \end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MLTL Regular Expressions} \label{regex}
We add to the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of a MLTL formula.
\begin{definition}[\emph{Temporal Regular Expression}]
Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$. Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula. We use the following operations to describe the form of satisfying computations of the formula in the bit string representation:
\begin{itemize}
  \item \emph{(Concatenation)} Denoted $RT$, this denotes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
%    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
    \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
    \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length. Note that in the bit string representation, $(,S^n)$, denotes a time step in which the truth value of all $n$ propositional variables does not matter.
    \item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
      \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$. %KYR: is this one relevant or should we take it out?
    \item We do not use the Kleene star since our computations are a fixed finite length.
\end{itemize}
\end{definition}
%An example of these operations follows.
\begin{example}
Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$). Clearly $T$ is the longer regex by one time step, so we concatenate $,S^2$ to the right of $R$. Thus $T =1S,1S | S1,S1$ and $R = S1,SS$. Now the regexes are the same length, so we can perform set intersection and alternation:
\begin{itemize}
    \item $R \land T = 11,1S | S1, S1$.
    \item $R \lor T = S1,SS | 1S,1S | S1,S1 = S1,SS | 1S,1S$.
\end{itemize}
\end{example}

For the purposes of describing the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\alpha, \beta$ well-formed MLTL formulas in negation normal form. We define the regular expression of satisfying computations for an MLTL formula as follows:

% ZILI: Failed attempt to get formulas side by side
% \begin{minipage}{0.45 \textwidth}
%     \begin{align}
%     &\text{reg}(\top) = S^n\\
%     &\text{reg}(\bot) = \emptyset \\
%     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
%     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
%     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
%     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta)
%     \end{align}
% \end{minipage}
% \begin{minipage}{0.55 \textwidth}
%     \begin{align}
%     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
%     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
%     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
%     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
%     \end{align}
% \end{minipage}

\begin{align}
     &\text{reg}(\top) = S^n\\
     &\text{reg}(\bot) = \emptyset \\
     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
\end{align}

 \subsection{Minimum Computation Length}
 These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\alpha)$, which is defined recursively below:
\begin{align}
    &\text{cplen}(p_k) = \text{cplen}(\neg p_k) = 1\\
    &\text{cplen}(\alpha \land \beta) = \text{cplen}(\alpha \lor \beta) = \max(\text{cplen}(\alpha), \text{cplen}(\beta))\\
    &\text{cplen}(\mathcal{G}_{[a,b]} \alpha) = \text{cplen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{cplen}(\alpha)\\
    &\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))
\end{align}

Intuitively, $\text{cplen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature. In \cite{KZJZR20}, $$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha), \text{cplen}(\beta))$$

whereas our minimum computation length for Until and Release is 
$$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{cplen}(\alpha)-1}, \text{cplen}(\beta)).$$
We provide the proof for the minimum computation length of Until and Release below.
\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\alpha, \beta$ be well-formed MLTL formulas in NNF. The minimum computation length of Until and Release is given by $\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))$.
\end{theorem}

\begin{proof}
The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\
 Recall that $\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$. Thus
 \begin{align*}
     \text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\alpha), i + \text{cplen}(\beta))\right)\\
     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta))\right)\\
     &= b + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta)).
 \end{align*}
 Now recall that $\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$. Thus
 \begin{align*}
     \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \beta), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
     &= \max\left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
     &= \max \left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\beta), i + \text{cplen}(\alpha))\right) \right)\\
     &= \max \left( b + \text{cplen}(\beta), \max(b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\right)\\
     &= \max(b + \text{cplen}(\beta), b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\\
     &= b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta)).
 \end{align*}
 This completes the proof.
 \end{proof}

@@

 \begin{theorem}[\emph{Soundness and Completeness}]
 For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
 \end{theorem}
 \begin{proof}
 We proceed by induction on the length of the formula.\\

@@

 \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
 If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$. Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

 \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
 Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

@@

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} >  \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} > \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \lor \text{''} + \alpha_{2} + \text{``)''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} > \alpha_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
    \]
%\end{adjustwidth}
\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} = \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} = \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = 
    \text{``((''} + \alpha_{1} + \text{``} \& \text{''} + \alpha_{2} + \text{``)}
    \lor 
    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2}) + \text{``))''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} = \alpha_{2})) =
    S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})) \; + \;  
    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2})).
    \]
%\end{adjustwidth}
\textbf{If} $\alpha$ \textbf{is} ``$\lor$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\lor [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \lor \alpha_{2}) \lor ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\lor$, we have that:
    \[
    S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}
\textbf{If} $\alpha$ \textbf{is} ``$\&$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\& [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \& \alpha_{2}) \& ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\&$, we have that:
    \[
    S(\text{\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}
\textbf{If} $\alpha$ \textbf{is} ``$=$ [$\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $= [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} = \alpha_{2}) = ... \alpha_{k})\text{''}.
    \]
Based on the space complexities of $\&$ and $\lor$, this gives:
    \[
    S(\text{\emph{reg}}(= [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i}))
